\LARGE \bf A Formal Description of Bitcoin's Script Language

### 2017-03-21 paper.tex
Added missing word

As the Bitcoin protocol lacks any formal specification by which it is defined, it is well accepted that the reference implementation defines the protocol. We therefore turned to the reference implementation to construct our description of Script's grammar---while also heavily upon the [Bitcoin Wiki] and [Mastering Bitcoin] to gain a detailed if not authoritative conceptual understanding of the relevant concepts and constructs. Insomuch as our grammar is consistent with this reference, it is correct. Insomuch as it diverges it is incorrect. Formally proving the consistency or equivalence of our grammar with the reference implementation is outside the scope of this project and is left as future work. Indeed, our grammar is purposefully incomplete as discussed below (\S II.C) due to the disproportionate expressive burden imposed by a few op-codes.
\subsubsection{Syntax}

>>>>

As the Bitcoin protocol lacks any formal specification by which it is defined, it is well accepted that the reference implementation defines the protocol. We therefore turned to the reference implementation to construct our description of Script's grammar---while also relying heavily upon the [Bitcoin Wiki] and [Mastering Bitcoin] to gain a detailed if not authoritative conceptual understanding of the relevant concepts and constructs. Insomuch as our grammar is consistent with this reference, it is correct. Insomuch as it diverges it is incorrect. Formally proving the consistency or equivalence of our grammar with the reference implementation is outside the scope of this project and is left as future work. Indeed, our grammar is purposefully incomplete as discussed below (\S II.C) due to the disproportionate expressive burden imposed by a few op-codes.
\subsubsection{Syntax}
